### 2022-05-31 main/chapter_2ljets.tex
add region defn tables for Hight and Int

\begin{figure}[tp]
\centering
\includegraphics[width=0.9\textwidth]{figures/2ljets_rjr_trees.pdf}
\caption{%
Decay trees for the $\twoljets$-RJR analysis.
\emph{This figure was made by the RJR team.}~\cite{atlas2022searches}.
Both diagrams represent processes which are targetted in the electroweak
analysis.
(left) A fully-resolved decay tree with its particles labelled.
(right) Only the $Z\rightarrow\ell\ell$ (\underline{V}ector boson)
is resolved, but the supersymmetric system recoils off
hard QCD jets labelled ``ISR'', boosting the \underline{I}nvisible particles,
to generate visibly large $\met$ in models with small mass-splittings.
The same approach is used for SR-OffShell selections in the electroweak
analysis.
}
\label{fig:2ljets_rjr_decay_trees}
\end{figure}

@@

All main regions are defined in Table~\TODO{tab}.
High regions are discussed in Section~\ref{sec:2ljets_high}.
Intermediate regions are discussed in Section~\ref{sec:2ljets_int}.
Low regions are discussed in Section~\ref{sec:2ljets_low}.
Off-shell regions are discussed in Section~\ref{sec:2ljets_high}.
Finally, these are combined into model-independent `Discovery' regions as
discussed in Section~\ref{2ljets_disco}.

@@

@@

>>>>

\begin{figure}[tp]
\centering
\includegraphics[width=0.9\textwidth]{figures/2ljets_rjr_trees.pdf}
\caption{%
Decay trees for the $\twoljets$-RJR analysis.
\emph{This figure was made by the RJR team.}~\cite{atlas2022searches}.
Both diagrams represent processes which are targetted in the electroweak
analysis.
(left) A fully-resolved decay tree with its particles labelled.
(right) Only the $Z\rightarrow\ell\ell$ \underline{V}ector boson)
is resolved, but the supersymmetric system recoils off
hard QCD jets labelled ``ISR'', boosting the \underline{I}nvisible particles,
to generate visibly large $\met$ in models with small mass-splittings.
The same approach is used for SR-OffShell selections in the electroweak
analysis.
}
\label{fig:2ljets_rjr_decay_trees}
\end{figure}

@@

\TODO{define presel, preselection SFOS 25 1j met>100 metsig>6}

High regions are discussed in Section~\ref{sec:2ljets_high}.
Intermediate regions are discussed in Section~\ref{sec:2ljets_int}.
Low regions are discussed in Section~\ref{sec:2ljets_low}.
Off-shell regions are discussed in Section~\ref{sec:2ljets_high}.
Control and validation regions are included in these sections near to their
targetted regions.
Finally, these are combined into model-independent `Discovery' regions as
discussed in Section~\ref{sec:2ljets_disco}.

@@

Table~\ref{tab:2ljets_high}.

\begin{table}[tp]
\footnotesize
\centering
\begin{tabular}{lcccccccc}
& $\njet$
& $\nbtag$
& $\metsig$
& $m_X/\eV[G]$
& $\Delta R_X$
\\[1em]
SR-High
& $\geq2$
& $\leq 1$
& $18\textrm{--}21\textrm{--}\infty$
& $\mjj \in 60\textrm{--}110$
&
$\rjj \in 0\textrm{--}0.8\textrm{--}1.6$
\\[.5em]
\quad VR-High
& $\geq2$
& $\leq 1$
& $> 18$
& $\heartsuit \mjj \in 20\textrm{--}60 \mid 60\textrm{--}110$
& $\rjj < 1.6$
\\[.5em]
\quad VR-High-R
& $\geq 2$
& $\leq 1$
& $> 18$
& $\heartsuit \mjj > 20$
& $\heartsuit \rjj > 1.6$
\\[1em]
SR-High-1J
&
$\hphantom{\geq}~1$
& $\leq 1$
& $> 12$
& $\mjetone \in 60\textrm{--}110$
&
\\[.5em]
\quad VR-High-1J
& $\hphantom{\geq}~1$
& $\leq 1$
& $> 12$
& $\heartsuit \mjetone \in 20\textrm{--}60 \mid 60\textrm{--}110$
&
\\[1em]
SR-$\ell\ell bb$
& $\geq 2$
& $\geq 2$
& $> 18$
& $\mbb \in 60\textrm{--}150$
&
\\[.5em]
\quad VR-$\ell\ell bb$
& $\geq 2$
& $\geq 2$
& $\heartsuit 12\textrm{--}18$
& $\mbb \in 60\textrm{--}150$
&
\end{tabular}
\small
\\[1em]
Common: presel, $\mll \in 71\textrm{--}111\,\eV[G]$, $\mttwo > 80\,\eV[G]$
\caption{%
% Overview of the High and Intermediate signal, control, and validations regions of the electroweak search.
%All regions except VR-SS require exactly two opposite-charge, same-flavour signal leptons with $\pt>25$~\eV[G]\ and $\met>100~\eV[G]$.
%Instead, VR-SS requires same-charge leptons.
% The main requirements that distinguish the control and validation regions from the signal regions are highlighted in boldface.
% The bracketed requirements denote the binning used in model-dependent fits, as described in the text.
Differences between regions are marked $\heartsuit$.
\TODO{}
}
\label{tab:2ljets_high}
\end{table}

@@

Table~\ref{tab:2ljets_int}.

\begin{table}[tp]
\footnotesize
\centering
\begin{tabular}{lcccccccc}
& $\njet$
& $\nbtag$
& $\metsig$
& $m_X/\eV[G]$
& $\ptjone/\eV[G]$
\\[1em]
SR-Int
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}15\textrm{--}18$
& $\mjj \in 60\textrm{--}110$
& $> 60$
\\[.5em]
\quad VR-Int
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}18$
& $\mjj \in 60\textrm{--}110$
& $\heartsuit < 60$
\\[1em]
CR-VZ
& $\geq 2$
& $\hphantom{\geq}~0$
& $12\textrm{--}18$
& $\heartsuit \mjj \in 20\textrm{--}60 \mid 60\textrm{--}110$
& $\heartsuit $
\\[.5em]
CR-tt
& $\geq 2$
& $\heartsuit \geq 1$
& $\heartsuit 9\textrm{--}12$
& $\heartsuit \mjj > 20$
& $> 60$
\end{tabular}
\small
\\[0.5em]
Common: presel, $\mll \in 81\textrm{--}101\,\eV[G]$, $\mttwo > 80\,\eV[G]$
\caption{%
% Overview of the High and Intermediate signal, control, and validations regions of the electroweak search.
%All regions except VR-SS require exactly two opposite-charge, same-flavour signal leptons with $\pt>25$~\eV[G]\ and $\met>100~\eV[G]$.
%Instead, VR-SS requires same-charge leptons.
% The main requirements that distinguish the control and validation regions from the signal regions are highlighted in boldface.
% The bracketed requirements denote the binning used in model-dependent fits, as described in the text.
Differences between regions are marked $\heartsuit$.
\TODO{}
}
\label{tab:2ljets_int}
\end{table}
